\documentclass[12pt]{article}

\usepackage[margin=0.5in]{geometry} % Change margins
\usepackage{xcolor} % Custom color
\usepackage{times} % Change font
\usepackage{nopageno}
\usepackage{enumitem} % Allow custom itemize bullet character

\usepackage[colorlinks = true,
            linkcolor  = blue,
            urlcolor   = blue,
            citecolor  = blue,
            anchorcolor= blue]{hyperref} % Links at top


\definecolor{textGray}{RGB}{75, 78, 80}
\newcommand{\sectionRule}{\textcolor{gray}{\rule{7.27in}{0.02cm}}}
\newcommand{\sectionTxt}[1]{\noindent\textbf{#1}\\}
\newcommand{\textDate}[3]{\noindent#1 $|$ #2 $|$ {\color{textGray} #3}}
\newcommand{\projText}[2]{\noindent#1 $|$ {\color{textGray} #2}}

% Squish the text together a bit
\linespread{0.5}


\begin{document}
    \begin{center}
        {\huge Yousef Al Hashemi}\vspace{0.5em}\\
        {\normalsize 647.972.2668 $|$ yousefalhashemi20@gmail.com}\\
        {\normalsize LinkedIn: \href{https://www.linkedin.com/in/yousefalhashemi}{linkedin.com/in/yousefalhashemi} $|$ GitHub: \href{https://github.com/Yalhash}{github.com/Yalhash}}\\
    \end{center}

    \sectionTxt{TECHNICAL SKILLS}
    \sectionRule \\


    {C++23, Python, Java, Typescript, TCL, C, Git, Bash, Linux, NestJS, SQL, Makefile, PERL} \\


    \sectionTxt{WORK EXPERIENCE}
    \sectionRule

    \textDate{Intel (Altera)}{Software Engineer}{July 2023 -- Current}
    \begin{small}
        \begin{itemize}
            \itemsep0em 

            % PCC
            \item {Worked on the compiled IP caching feature, enabling users to accelerate users' design iteration time.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {Introduced flow-level runtime optimizations and parallelized cache generation achieving a 40\% speedup in the cached synthesis flow.}
                    \item {Created a testing plan and infrastructure to track and resolve runtime issues in the flow.}
                    \item {Polished the feature to production quality through rigorous testing and collaboration with multiple teams.}
                \end{itemize}

            % MISC
            \item {Reduced memory usage in GUI use cases by 50\%.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {The benchmark customer designs saved upwards of 6GB of RAM.}
                    \item {Stopped the GUI from being unresponsive and frequently freezing.}
                    \item {Used memory profiling to trace the issue throught a convoluted event-based flow which doubled the memory.}
                \end{itemize}

            % DMS
            \item {Owned and extended the database management system.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {Found, diagnosed, and replaced faulty concurrency locking mechanism with a more robust and better tested implementation.}
                    \item {Improved thread safety and multi-process safety of the system, enabling new multi-process flows.}
                \end{itemize}

            % Preserve
            \item {Implemented the design partition Preserve feature, enabling users to speed up user design iteration time.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {Users can block off sections of their designs which meet design requirements save the compilation results.}
                    \item {Subsequent compilations with preserved partitions become faster proportional to the amount of the design preserved.}
                    \item {Coordinated with other teams across flows to ensure compliance with the feature.}
                    \item {Defined and executed testing plan for the feature.}
                \end{itemize}


            %UNO
            \item {Owned and extended features for the internal netlist writer.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {Enabled several production features, is still in active use, and still extended for new use cases.}
                    \item {Updated and expanded the writer to allow the output of scripting languages.}
                    \item {Directed the development of adding TCL, Python, and VHDL output to the writer.}
                \end{itemize}

        \end{itemize}
    \end{small}


    \textDate{Questrade}{Full Stack Engineer Intern}{May 2022 -- Aug 2022}
    \begin{small}
        \begin{itemize}
            \itemsep0em 
            \item {Wrote a REST API endpoint in Typescript with NestJS to fetch information from an internal SQL database.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {Designed the OpenAPI YAML specification for this endpoint and another in the same domain.}
                    \item {Added authentication to ensure users had proper access permissions.}
                \end{itemize}
            \item {Investigated dropped messages in the high-speed messaging system.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {Set up infrastructure to collect relevant statistics.}
                    \item {Collaborated with other teams to implement solutions.}
                \end{itemize}
        \end{itemize}
    \end{small}

    \textDate{Intel}{Software Engineering Intern}{May 2020 -- Aug 2021}
    \begin{small}
        \begin{itemize}
            \itemsep0em 
            \item {Created the internal netlist writer in C++ which converts internal data structure into hardware code.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {Used to verify the functional correctness of modifications made to the internal data structure.}
                \end{itemize}
            \item {Brought a Python based analytics service online which had been down for 6 months.}
            \item {Collaborated on a graph visualization software which took netlist data files and displayed them.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {Allowed users working with the data files to query custom paths and understand their work better.}
                \end{itemize}
            \item {Created a build time script to consolidate and convert legacy XML data into new updated formats.}
        \end{itemize}
    \end{small}

    \newpage

    \sectionTxt{PROJECT WORK}
    \sectionRule
    
    \projText{BlockFund}{July 2025 -- Current}
    \begin{small}
        \begin{itemize}
            \itemsep0em 
            \item {Created an Ethereum Smart Contract as a way to securely crowdfund projects in a decentralized manner.}
            \item {Works with the native token, with options for users to specify ERC20 tokens, or mixed ERC20 and Native donations.}
            \item {Utilizes Uniswap to compare prices between tokens and verify when the project goal is met.}
        \end{itemize}
    \end{small}

    \projText{RoomE - Capstone}{Sept 2021 -- Mar 2022}
    \begin{small}
        \begin{itemize}
            \itemsep0em 
            \item {Worked in a team of peers to create an autonomous robot which explores indoor environments, creates maps of them using LIDAR, and uploads them to a website where they could be viewed.}
            \item {Created the code to solve pathfinding, SLAM, frontier exploration, create the data model and representation, and serial communication with the drive train. }
        \end{itemize}
    \end{small}

    \projText{Automated Clipping Channel}{Jun 2019 -- Jul 2019}
    \begin{small}
        \begin{itemize}
            \itemsep0em
            \item {Wrote a web scraper that finds popular video clips from Twitch.tv and edits them into a 10 minute video.}
            \item {Created in Python using Selenium to scrape the dynamic pages, and used FFMPEG to edit the video together.}
        \end{itemize}
    \end{small}

    \sectionTxt{EDUCATION}
    \sectionRule

    \textDate{Bachelor of Applied Science, Computer Science}{McMaster University}{Sept 2018 -- May 2023}
    \begin{small}
        \begin{itemize}
            \itemsep0em 
            \item Cumulative GPA: {11.5/12}
            \item Graduated Summa Cum Laude
            \item Relevant Coursework: {Data structures and Algorithms, Concurrent Systems, Principles of Programming, Databases, Algorithms and Complexity, Intro to Machine Learning, Computer Networks and Security, Operating Systems}
        \end{itemize}
    \end{small}


\end{document}
